A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-11-03 appendix.tex
dusty epicycles are not real, move to appendix

We eliminate the velocity perturbations to obtain
\begin{align}
  \left(\ii \zeta \sigma - \tstop c_s^2 \tepsilon |\bm{k}|^2\right)Q &=
  \ii \left[
  \frac{P}{\rho}\sigma + k_x\tstop c_s^2 F_r\left(1 -
  2\tepsilon\right)\right]W, \\
   \sigma^2 \left( \kappa^2 - \sigma^2 - \ii k_x F_r\right)W &=
    \left(k_z^2\kappa^2 - \sigma^2|\bm{k}|^2\right)Q, 
\end{align}
which yields the dispersion relation
\begin{align}
  &\frac{\zeta}{c_s^2|\bm{k}|^2}\sigma^5 + \ii \tepsilon \tstop
  \sigma^4 - \left[ \frac{\zeta}{c_s^2|\bm{k}|^2} \left(\kappa^2 - \ii
  k_x F_r\right) + \left(1 - \tepsilon\right)\right]\sigma^3 - \ii
  \tstop \left[\tepsilon \kappa^2 - \ii k_x F_r\left( 1 -
  \tepsilon\right)\right]\sigma^2 \notag\\ 
  &+ \left(1 -
  \tepsilon\right)\left(\frac{k_z\kappa}{|\bm{k}|}\right)^2\sigma +
  k_x \tstop F_r\left(1 - 2\tepsilon\right)
  \left(\frac{k_z\kappa}{|\bm{k}|}\right)^2  = 0.\label{streaming_dispersion}
\end{align}
The equation of state $P = c_s^2\left( 1 - \tepsilon\right)\rho$
was used. If we now set $\zeta = 0$ or consider $c_s^2\to \infty$ to
obtain the 
incompressible limit, and define $\tau_\mathrm{s} \equiv
\tstop/\left(1 - \tepsilon\right)$, we obtain: 
\begin{align}
\ii \tepsilon \tau_\mathrm{s}
  \sigma^4 - \sigma^3 - 
  \tau_\mathrm{s} \left[ \ii \tepsilon \kappa^2 + k_x F_r\left( 1 -
  \tepsilon\right)\right]\sigma^2 
  + \left(\frac{k_z\kappa}{|\bm{k}|}\right)^2\sigma + 
  k_x \tau_\mathrm{s} F_r\left(1 - 2\tepsilon\right)
  \left(\frac{k_z\kappa}{|\bm{k}|}\right)^2  = 0,\label{streaming_incompressible}
\end{align}
as derived by \cite{jacquet11} and \cite{laibe14} for the streaming
instability. If $|\sigma|/\OmK = O(\tau_\mathrm{s}\OmK)$ and
$\tau_\mathrm{s}\OmK\ll 1$, then the quartic term
is small and may be neglected. In that case we obtain the cubic
dispersion relation of \citet{youdin05a}.

>>>>

We eliminate the velocity perturbations to obtain
\begin{align}
  \left(\ii \zeta \sigma - \tstop c_s^2 \tepsilon |\bm{k}|^2\right)Q &=
  \ii \left[
  \frac{P}{\rho}\sigma + k_x\tstop c_s^2 F_r\left(1 -
  2\tepsilon\right)\right]W, \\
   \sigma^2 \left( \kappa^2 - \sigma^2 - \ii k_x F_r\right)W &=
    \left(k_z^2\kappa^2 - \sigma^2|\bm{k}|^2\right)Q, 
\end{align}
which yields the dispersion relation
\begin{align}
  &\frac{\zeta}{c_s^2|\bm{k}|^2}\sigma^5 + \ii \tepsilon \tstop
  \sigma^4 - \left[ \frac{\zeta}{c_s^2|\bm{k}|^2} \left(\kappa^2 - \ii
  k_x F_r\right) + \left(1 - \tepsilon\right)\right]\sigma^3 - \ii
  \tstop \left[\tepsilon \kappa^2 - \ii k_x F_r\left( 1 -
  \tepsilon\right)\right]\sigma^2 \notag\\ 
  &+ \left(1 -
  \tepsilon\right)\left(\frac{k_z\kappa}{|\bm{k}|}\right)^2\sigma +
  k_x \tstop F_r\left(1 - 2\tepsilon\right)
  \left(\frac{k_z\kappa}{|\bm{k}|}\right)^2  = 0.\label{streaming_dispersion}
\end{align}
The equation of state $P = c_s^2\left( 1 - \tepsilon\right)\rho$
was used.

\subsection{Incompressible limit}

 We can set $\zeta = 0$ or consider $c_s^2\to \infty$ to
obtain the incompressible limit. Using $\tau_\mathrm{s} \equiv
\tstop/\left(1 - \tepsilon\right)$, we obtain: 
\begin{align}
\ii \tepsilon \tau_\mathrm{s}
  \sigma^4 - \sigma^3 - 
  \tau_\mathrm{s} \left[ \ii \tepsilon \kappa^2 + k_x F_r\left( 1 -
  \tepsilon\right)\right]\sigma^2 
  + \left(\frac{k_z\kappa}{|\bm{k}|}\right)^2\sigma + 
  k_x \tau_\mathrm{s} F_r\left(1 - 2\tepsilon\right)
  \left(\frac{k_z\kappa}{|\bm{k}|}\right)^2  = 0,\label{streaming_incompressible}
\end{align}
as derived by \cite{jacquet11} and \cite{laibe14} for the streaming
instability. 
If $|\sigma|/\OmK = O(\tau_\mathrm{s}\OmK)$ and
$\tau_\mathrm{s}\OmK\ll 1$, then the quartic term
is small and may be neglected. In that case we obtain the cubic
dispersion relation of \citet{youdin05a}.

\subsection{Spuriously growing epicycles}

A caveat of the dispersion relations 
Eq. \ref{streaming_dispersion} and \ref{streaming_incompressible} is
that they admit spurious unstable modes with $|\sigma|\gtrsim \Omega$
that violates the one-fluid framework used in this
paper. We demonstrate this below by considering the
incompressible dispersion relation. (We checked numerically that
compressibilty has negligible effects on the modes examined.)

Consider the limit $k_z=0$. Then Eq. \ref{streaming_incompressible}
becomes 
\begin{align}      %streaming_incompressible
\ii \sigma^2 - \frac{\sigma}{\epsilon \tstop}  - \left(\ii \kappa^2 +
  \frac{k_xF_r}{\epsilon}\right) = 0. \label{kz_zero_si}
\end{align} 
Neglecting the quadratic term leads to stability, $\imag{\sigma}<0$, 
as found by \cite{youdin05a} in their full two-fluid analysis as 
$k_z\to0$.  
% However, the real and imaginary parts of Eq. \ref{kz_zero_si}  are
% \begin{align}
% \omega\left(2 s + \frac{1}{\epsilon\tstop}\right) - \frac{k_xF_r}{\epsilon} & =
%                                                                      0, \label{epi_overs1} \\
% \omega^2 - s^2 - \frac{s}{\epsilon\tstop}  - \kappa^2 &= 0, \label{epi_overs2}
% \end{align}
% so the growth rate satisfies 
% \begin{align*}
% \left( \frac{k_xF_r\tstop}{1 + 2 s\epsilon\tstop}\right)^2 - s^2
%   - \frac{s}{\epsilon \tstop} = \kappa^2. %\omega = \frac{k_xF_r\tstop}{1 + 2 s\epsilon\tstop}
% \end{align*} 
However, solving Eq. \ref{kz_zero_si} explicitly assuming $\epsilon s \tstop \ll 1$ would yield 
\begin{align}
  |\omega| &\simeq \left|k_xF_r\right| \tstop \sim \kappa, \\
  s &\simeq \epsilon \tstop \left[\left(k_xF_r\tstop\right)^2 - \kappa^2\right],\label{epi_grow}
\end{align}
Accordingly, given $k_xF_r$, growth is possible if 
\begin{align}
\tstop > \frac{\kappa}{k_x\left|F_r\right|}\equiv t_{\mathrm{s}0}.\label{epi_grow_criterion}
\end{align}
The mode is marginally stable when $\tstop =
t_{\mathrm{s}0}$. Alternatively, for fixed $\tstop$ growth is enabled
by a sufficiently large $k_xF_r$. Unlike the streaming instability,
which is strongly surpressed when $\epsilon=1$, these modes can still
grow at equal dust-to-gas ratio.

These growing epicycles have $|\omega|\gtrsim \kappa$. 
However, these modes are absent in full two-fluid
models \citep{youdin05a}. The discrepency lies in the fact that the
first-order  one-fluid equations are only valid for low-frequency waves with
$|\omega|\lesssim \Omega$. Thus only 
low-frequency modes should be retained from analyses based on the
first-order one-fluid approximation.

%When this is violated,
%terms of $O(\tstop^2)$ should be retained in deriving the one-fluid
%equations (Eq. \ref{masseq}---\ref{tempeq}).

Fig. \ref{dusty_growth1} show unstable modes found from
Eq. \ref{streaming_dispersion} as a function of $K_z$ at fixed $K_x 
= 1500$, $\epsilon=2$ and $\taus\OmK=0.01$.  
The (spurious) overstable dusty epicycles' growth
rates are weakly depedent on $K_z$ and are well approximated by
that in the $K_z=0$ limit, Eq. \ref{epi_grow}, which becomes 
\begin{align*} 
  s = \epsilon \left(1 - \tepsilon
  \right)\taus\OmK^2\left[4K_x^2\left(1-\tepsilon\right)^4\left(\taus\OmK\right)^2
  -1 \right]
\end{align*}
in the above notation. 
For the case considerd in Fig. \ref{dusty_growth1} we find
$s\simeq0.067\OmK$, as observed. By contrast, the streaming
instability requires $K_z>0$, and dominates when
$K_z\gtrsim 100$.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/streaming2}
  \caption{Growth rates of dust-drag instabilities with fixed radial
    wavenumber and dust-to-gas ratio, as a function of
    the vertical wavenumber at fix stopping time. \label{dusty_growth1}
  }
\end{figure}

Caution must be taken if the first-order one-fluid equations are used
to simulate dusty gas. 
%One should ensure that the physical dust-gas instabilty
%(which should have low-frequency in order for the first-order one-fluid
%approximation) has a larger growth rate than that of the spurious
%modes, which is given by Eq. \ref{epi_growth}. 
%Fig. \ref{dusty_growth1} suggests that the
%streaming instability would dominate, provided there is sufficient
%resolution to resolve high $K_z$ modes.  
For example, 2D, razor-thin disks would allow the spurious epicycles
to dominate, since in that case the streaming instability cannot
operate. Fig. \ref{dusty_growth1} suggest that in a realistic 3D disks
where a range of $K_z$ is allowed, the streaming instability should
dominate.

Thus simulations based on the first-order one-fluid equations should
be set up to surpress these spurious epicycles. This might be
achieved, for example, through physical or numerical viscosity to
eliminate high-$k_x$ modes, since for fixed disk/dust parameters these
spurious epicycles only operate at sufficiently small radial
wavelengths. Alternatively, one needs to ensure the physical
instabilities of interest have larger growth rates than the spurious
epicycles.

%An important caveat is that the one-fluid approximation for dusty gas 
%may not hold well when $|\omega| \gtrsim 
%\Omega$ \citep{youdin05a}, as is the case for dusty epicycles.

% Their
% existence should be checked with full dust-plus-gas 
% simulations. Several 2D, razor-thin disk simulations do suggest a
% dusty instability that destory vortices
% \citep{fu14b,raettig15,surville16}. These setups are significantly
% more complex than our models, but \citeauthor{raettig15} did find 
% particle clumping in a test simulation without a vortex. These results
% might be related to the overstable dusty epicycles discussed here.

% Real disks are three-dimensional, so the importance of dusty 
% epicycles should be compared with $k_z\neq0$ modes, which
% includes the classic streaming instability \citep{youdin05a},
% discussed next.

%\subsection{Numerical example}

% In Fig. \ref{dusty_growth2} we fix the wavenumbers and vary the
% stopping time. The vertical dashed line is the critical stopping time
% for the overstable dusty epicycles, Eq. \ref{epi_grow_criterion},
% which is  
% \begin{align*}
%   \tau_{\mathrm{s,min}}\OmK = \frac{1}{2K_x\left(1-\tepsilon\right)^2} 
% \end{align*}
% in the above notation. For this example, $\tau_{\mathrm{s,min}}\OmK\simeq 
% 0.003$, as observed. On the other hand, the streaming instability
% shows weak dependence on $\taus$ for this range of stopping times 
% (it ultimated vanishes as $\taus\to0$).

% \begin{figure}
%   \includegraphics[width=\linewidth]{figures/streaming3}
%   \caption{Growth rates of dust-drag instabilities with fixed radial
%     wavenumber and dust-to-gas ratio, as a
%     function of stopping time at fixed vertical wavenumber. The
%     vertical dashed line correspond to the minimum stopping time for
%     growth of the dusty epicycle, given by
%     Eq. \protect\ref{epi_grow_criterion}. \label{dusty_growth2}
%   }
% \end{figure}

% These calculations suggest that in a realistic 3D dusty disk where
% vertical motions are allowed, the classic streaming
% instability is dominant because there exists $K_z$ values for which it
% dominates. This also renders the uncertainties in the  
% approximations used to describe the dusty epicycle modes
% irrelevant. On the other hand, the one-fluid framework can capture the
% streaming instability in the appropriate limit, as seen in Table
% \ref{si_compare}.

%For small growth rates the real frequency $|\omega| =  
%O(\kappa)$, so these are overstable epicycles.

%We finally note that Eq. \ref{epi_overs1}---\ref{epi_overs2} 
%admit pure oscillations with $s \equiv 0$, $\omega = 
%\pm\kappa$ if 
%\begin{align}
%  \tstop = \frac{\kappa}{k_x\left|F_r\right|}. 
%\end{align}
%This is the condition for marginal stability.

% However, retaining all the terms (but still in the incompressible
% limit) can yield instability, as follows. Eq. \ref{kz_zero_si} admit
% pure oscillations with $\sigma = -\omega$ when 
% \begin{align*}
%   \omega &= \pm \kappa, \\
%   \tstop & = \frac{\omega}{ k _x F_r }
%          \equiv t_{\mathrm{s}0}.
% \end{align*} 
% Since $\tstop\geq 0$, we require $k_xF_r > 0$ if $\omega = \kappa$;
% and $k_xF_r < 0$ if $\omega = -\kappa$. For $k_x>0$ these marginally
% stable epicycles require radial pressure gradients decreasing and increasing
% outwards, respectively.

%We require $\omega/k_xF_r> 0$

% We now perturb about this state of marginal stability by writing
% $\sigma = \dd \sigma - \omega $ with $\dd\sigma = \ii\dd s -
% \dd\omega$, $\tstop = t_{\mathrm{s}0} +
% \dd\tstop $, and assume the $\dd$ quantities are small in
% magnitude. Then 
% \begin{align*} 
% \dd s = \frac{2\epsilon \kappa^2 }{1 +
%   4\epsilon^2 t_{\mathrm{s}0}^2\kappa^2}\dd \tstop. 
% \end{align*}
% Thus given $k_xF_r$, there exist growing modes 
% when the stopping time is slightly larger than
% $t_{\mathrm{s}0}$.

% %{\bf note: several approx used}

% If we instead fix $\tstop$ and vary $k_xF_r$ about marginal stability,
% a similar exercise yields  
% \begin{align*} 
%   \dd s = \frac{\epsilon \tstop^3}{1 +
%   4\epsilon^2 \tstop^2 \kappa^2}\dd \left(k_x^2F_r^2\right).  
% \end{align*}
% Thus it is possible to destabilize the system by slightly increasing
% $|k_xF_r|>\kappa/ \tstop$ (i.e. shorter radial wavelengths and/or
% stronger pressure gradients).

### 2016-11-03 linear.tex
dusty epicycles are not real, move to appendix

\section{Dust-drag instabilities}\label{si}
In the special case of an unstratified disk (neglecting the vertical
component of the stellar gravity), we may also Fourier analyze in $z$
to obtain an algebraic dispersion relation of the form  
$\sum_{j=0}^{5}c_j(k_x,k_z)\sigma^j = 0$, where $k_z$ is a real
vertical wavenumber. The coefficients $c_j$ can be read 
off Eq. \ref{streaming_dispersion} in  Appendix \ref{compressible_streaming}. 
There we also show that this dispersion relation reduces to that for
the streaming instability (SI) in the limit of incompressible gas and small
$\tstop$ \citep{youdin05a,jacquet11}.

\subsection{Overstable epicycles}
If we further consider the limit $k_z=0$, the incompressible dispersion
relation, Eq. \ref{streaming_incompressible}, reduces to 
\begin{align}      %streaming_incompressible
\ii \sigma^2 - \frac{\sigma}{\epsilon \tstop}  - \left(\ii \kappa^2 +
  \frac{k_xF_r}{\epsilon}\right) = 0. \label{kz_zero_si}
\end{align} 
%Here we use $\tau_\mathrm{s}=\tstop/(1-\tepsilon)$ for convenience. 
If the quadratic term is neglected, then $\imag{\sigma}<0$, implying
stability, as concluded by \cite{youdin05a}.

However, retaining all the terms (but still in the incompressible
limit) can yield instability, as follows. Eq. \ref{kz_zero_si} admit
pure oscillations with $\sigma = -\omega$ when 
\begin{align*}
  \omega &= \pm \kappa, \\
  \tstop & = \frac{\omega}{ k _x F_r }
         \equiv t_{\mathrm{s}0}.
\end{align*} 
Since $\tstop\geq 0$, we require $k_xF_r > 0$ if $\omega = \kappa$;
and $k_xF_r < 0$ if $\omega = -\kappa$. For $k_x>0$ these marginally
stable epicycles require radial pressure gradients decreasing and increasing
outwards, respectively.

%We require $\omega/k_xF_r> 0$

We now perturb about this state of marginal stability by writing
$\sigma = \dd \sigma - \omega $ with $\dd\sigma = \ii\dd s -
\dd\omega$, $\tstop = t_{\mathrm{s}0} +
\dd\tstop $, and assume the $\dd$ quantities are small in
magnitude. Then 
\begin{align*} 
\dd s = \frac{2\epsilon \kappa^2 }{1 +
  4\epsilon^2 t_{\mathrm{s}0}^2\kappa^2}\dd \tstop. 
\end{align*}
Thus given $k_xF_r$, there exist growing modes 
when the stopping time is slightly larger than
$t_{\mathrm{s}0}$.

%{\bf note: several approx used}

If we instead fix $\tstop$ and vary $k_xF_r$ about marginal stability,
a similar exercise yields  
\begin{align*} 
  \dd s = \frac{\epsilon \tstop^3}{1 +
  4\epsilon^2 \tstop^2 \kappa^2}\dd \left(k_x^2F_r^2\right).  
\end{align*}
Thus it is possible to destabilize the system by slightly increasing
$|k_xF_r|>\kappa/ \tstop$ (i.e. shorter radial wavelengths and/or
stronger pressure gradients).

\citep[cf. the `convective overstability', ][]{klahr14,lyra14,latter16}.

\subsection{Streaming instability}

@@

We now consider the streaming instability with $k_z\neq 0$. 
We solve Eq. \ref{streaming_dispersion} for selected cases where SI  
growth rates have been 
calculated analytically from full two-fluid disk models and measured 
from direct numerical particle-gas simulations 
\citep[namely][]{youdin07b,bai10b}. These authors use normalized
wavenumbers $K_{x,z} = \eta r k_{x,z}$ where
\begin{align} 
  \eta \equiv -\frac{1}{2\rhog r\OmK^2}\frac{\p P}{\p r} = 
  \frac{1}{2\left(1-\tepsilon\right)}\frac{F_r}{r\OmK^2}, 
\end{align} 
measures the pressure offset of Keplerian rotation. We use
$\eta=0.05c_s/r\OmK$. They also define the stopping time as
$\tau_\mathrm{s}=\tstop/(1-\tepsilon)$.

@@

\subsection{Numerical example}

To demonstrate the above instabilities we numerically solve the
full dispersion relation, Eq. \ref{streaming_dispersion} at fixed $K_x
= 1500$ and $\tepsilon=2$. Growth rates are shown in 
Fig. \ref{dusty_growth} as a function of $K_z$ at fixed $\taus\OmK=0.01$
(top panel, which includes `linC' in Table \ref{si_compare}); and as a
function of $\taus\OmK$ at fixed $K_z=50$ (bottom panel).

The top panel shows that the streaming instability vanishes as
$K_z\to0$, but it dominates most of $K_z$
-space. The overstable epicycles become important for 
$K_z\lesssim 100$, but their growth rates are weak. We thus
expect streaming instabilities to dominate, provided small
lengthscales can be resolved.

In the bottom panel we confirm that the overstable epicycles require a
sufficiently large stopping time at fixed wavenumbers. The vertical
dashed line is the critical stopping time 
\begin{align*}
  \tau_{\mathrm{s}0}\OmK = \frac{1}{2K_x\left(1-\tepsilon\right)^2} 
\end{align*}
in the above notation. For this example, $\tau_{\mathrm{s}0}\OmK\simeq
0.003$, as observed. On the other hand, the streaming instability
shows weak dependence on $\taus$ for this range of stopping times.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/streaming2}
  \includegraphics[width=\linewidth]{figures/streaming3}
  \caption{Growth rates of dust-drag instabilities with fixed radial
    wavenumber and dust-to-gas ratio, as a function of
    the vertical wavenumber at fix stopping time (top); and as a
    function of stopping time at fixed vertical wavenumber (bottom).  
\label{dusty_growth}
  }
\end{figure}

>>>>

\section{Streaming instability}\label{si}
In the special case of an unstratified disk (neglecting the vertical
component of the stellar gravity), we may also Fourier analyze in $z$
to obtain an algebraic dispersion relation of the form  
$\sum_{j=0}^{5}c_j(k_x,k_z)\sigma^j = 0$, where $k_z$ is a real
vertical wavenumber. The coefficients $c_j$ can be read 
off Eq. \ref{streaming_dispersion} in  Appendix \ref{compressible_streaming}. 
There we also show that this dispersion relation reduces to that for
the streaming instability (SI) in the limit of incompressible gas and small
$\tstop$ \citep{youdin05a,jacquet11}.

\subsection{Numerical examples}

@@

%We now consider the streaming instability with $k_z\neq 0$. 
We solve the full dispersion relation, Eq. \ref{streaming_dispersion} for selected cases where SI  
growth rates have been 
calculated analytically from full two-fluid disk models and measured 
from direct numerical particle-gas simulations 
\citep[namely][]{youdin07b,bai10b}. These authors use normalized
wavenumbers $K_{x,z} = \eta r k_{x,z}$ where
\begin{align} 
  \eta \equiv -\frac{1}{2\rhog r\OmK^2}\frac{\p P}{\p r} = 
  \frac{1}{2\left(1-\tepsilon\right)}\frac{F_r}{r\OmK^2}, 
\end{align} 
measures the pressure offset of Keplerian rotation. We use
$\eta=0.05c_s/r\OmK$. They also define the stopping time as
$\tau_\mathrm{s}=\tstop/(1-\tepsilon)$.

@@

\subsection{Comparison to the convective overstability}
%These slowly-growing modes have $|\omega|\simeq \kappa$, so they correspond to
%overstable epicycles. 
The streaming
instability bears some similarity  to the `convective 
overstability' in dust-free, non-isothermal disks 
\citep{klahr14,lyra14,latter16}. In that case, the combination of an 
unstable radial entropy gradient ($N_r^2  \propto \p_rP\p_rS < 0 $) and
finite thermal relaxation time leads to epicyclics with
growth rate $\propto  -N_r^2$

Indeed, the effective radial buoyancy frequency in our dusty disk 
with negligble background density gradient is unstable, 
\begin{align}
  N_r^2 \equiv F_r\frac{\p S_\mathrm{eff}}{\p r} =
  -\frac{\rho}{P}F_r^2<0.  
\end{align}
Convective overstability cannot exist in our locally isothermal disks,
which have zero cooling times. On the other hand, dust-gas drag 
is equivalent to heating/cooling in our framework.

One might then think of the streaming instability as a dusty relative
to the convective  overstability. Explicit solutions in the small
$\tstop$ limit show that streaming instability growth rates are
also $\propto |N_r^2|$  \citep{jacquet11}, as is for the convective
overstability \citep{lyra14}. Furthermore, both instabilities require
finite effective cooling times, and both require $k_z\neq0$. 
{\bf note: si osc freq not too small compared to kappa}

However, the convective overstability is most unstable at $k_x=0$
\citep{latter14}  whereas the streaming instability growth rate is maximized at finite $k_x$
\citep{youdin05a}. Nevertheless, they share the same underlying
physical mechanism, i.e. pressure-density phase lags.
